### 2013-03-14 au_topology_seminar_talk_2013_02_18.tex
updated todos

\begin{proof}
Take a zero-dimensional Corson compact $Y$ of weight $2^\omega$, which is not Eberlein compact. (See Todercevic \cite{Todercevic} for an example.) It follows by \cite{G1} that $Y^2$ is hereditarily metaLindel\"of, but not hereditarily $\sigma$-metacompact. Let $X$ be a non-$\sigma$-metacompact subset of $Y^2$, and let $\mc{V}$ be an open cover of $X$ such that no $\sigma$-point-finite open refinement exists.

Let $\mc{B}$ be a clopen base for $X$ of cardinality $2^\omega$ which is a refinement of $\mc{V}$.  Then as $X$ is metaLindel\"of, locally Lindel\"of, and regular, by Thm \ref{michael}, let $\mc{U}\subseteq \mc{B}$ be a point-countable clopen refinement of $\mc{V}$ of cardinality $2^\omega$, which cannot be $\sigma$-point-finite.
\end{proof}

\begin{definition}
Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $2^\omega$, and add open (in fact, compact) neighborhoods of the form: 
  \[
    B_c = c \cup (U_c \times \{c\rest n : n < \omega\})
  \]
as seen in Figure \ref{fig:cantor_tree}.
\end{definition}

>>>>

\begin{proof}
Take a zero-dimensional Corson compact $Y$ of weight $2^\omega$, which is not Eberlein compact. (See Todercevic \cite{Todercevic} for an example.) It follows by \cite{G1} that $Y^2$ is hereditarily metaLindel\"of, but not hereditarily $\sigma$-metacompact. Note $X=Y^2\setminus \Delta$ is an open non-$\sigma$-metacompact subspace of $Y^2$, and thus locally compact, and let $\mc{V}$ be an open cover of $X$ such that no $\sigma$-point-finite open refinement exists.

Let $\mc{B}$ be a clopen base for $X$ of cardinality $\leq 2^\omega$ which is a refinement of $\mc{V}$.  Then as $X$ is metaLindel\"of, locally Lindel\"of, and regular, by Thm \ref{michael}, let $\mc{U}\subseteq \mc{B}$ be a point-countable clopen refinement of $\mc{V}$ of cardinality $2^\omega$, which cannot be $\sigma$-point-finite.

% TODO finish this for \leq 2^\omega
\end{proof}

\begin{definition}
Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $\leq 2^\omega$, and add open (in fact, compact) neighborhoods of the form: 
  \[
    B_c = c \cup (U_c \times \{c\rest n : n < \omega\})
  \]
as seen in Figure \ref{fig:cantor_tree}.
\end{definition}
